plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-10-11 manuscript.Rmd
README update and minor cleanup

# Find current SHA of plantecophys
rep_pkg <- "c:/repos/plantecophys"
if(file.exists(rep_pkg)){
  pkgrep <- repository(rep_pkg)
  r <- reflog(pkgrep, verbose=FALSE)
  cur_sha <- substr(r[[1]]@sha, 1, 7)
} else {
  cur_sha <- "???"
}

>>>>

# Find current SHA of plantecophys (gives '???' on fail)
cur_sha <- get_git_SHA("c:/repos/plantecophys")
